Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-15 sections/observations.tex
15X5 lightcurve figure
Tight Layout change
scaling figures to 0.93/textwidth
Spell check and commas

%% Put combined firue here, and adjust width to keep us at 4 pages
\begin{figure}[h]
    \includegraphics[width=0.6\textwidth]{figures/LightcurveComparison.pdf}
    \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.}
\end{figure}

@@

To better understand the features of our radio data, we need an optical lightcurve for comparison.
Ideally, the optical lightcurve would be observed from the same location as our radio telescope in order for us to compare contact times, the depth of the eclipse, and the shape of the lightcurve.
Fortunately, Dr. Scott Austin used the UCA observatory across the street from our location to livestream the eclipse using a solar filter-equipped camera mounted to the observatory telescope.
Another experiment near our location led by Dr. Todd Abel and UCA Student Shane Ayotte used a Vernier Light Sensor (LS-BTA) pointed straight up at the sky to measure overall sky brightness.
\paragraph{The Livestream Lightcurve}
The livestream of the solar eclipse was captured by Dr. Scott Austin using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
This solar filter was removed during totality, marked by 2460409.2849 JD and 2460409.2884 JD.
This setup was attached to a Meade-14 LX200R on a Paramount MX+ equatorial mount to track the sun across the sky.
To transform the livestream into a lightcurve, we needed to extract the percentage of the sun's disk visible in the video frames as the eclipse progressed.
We accomplished this by first grayscaling the image of the eclipse and then using Otsu thresholding to only count pixels above a certain value.
This sucessfully counted the bright sun pixels while ignoring the background noise.
To get the time for each data point, we took an image of the in-video clock at the same time we counted the pixels of the eclipse and used computer vision to recognise the characters in the clock, giving us the time at which the frame was pixel-counted.
The number of pixels of the solar disk over time can then be normalized to a relative brightness.
\paragraph{The Light Sensor Lightcurve}
The light sensor used to collect data during the solar eclipse was the Vernier Light Sensor (LS-BTA) pointed at the sky.
Dr. Todd Abel and Shane Ayotte provided the light sensor data, which we normalized to relative brightness.
Because the light sensor data had timestamps included, we used it to confirm the timing accuracy of our other lightcurves.
\\
Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.

>>>>

%% Put combined firue here, and adjust width to keep us at 4 pages
\begin{figure}[h]
    \includegraphics[width=0.93\textwidth]{figures/LightcurveComparison.pdf}
    \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.}
\end{figure}

@@

To better understand the features of our radio data, we need an optical lightcurve for comparison.
Ideally, the optical lightcurve would be observed from the same location as our radio telescope in order for us to compare contact times, the depth of the eclipse, and the shape of the lightcurve.
Fortunately, Dr. Scott Austin used the UCA observatory across the street from our location to livestream the eclipse using a solar filter-equipped camera mounted to the observatory telescope.
Another experiment near our location, led by Dr. Todd Abel and UCA Student Shane Ayotte, used a Vernier Light Sensor (LS-BTA) pointed straight up at the sky to measure overall sky brightness.
\paragraph{The Livestream Lightcurve}
The livestream of the solar eclipse was captured by Dr. Scott Austin using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
This solar filter was removed during totality, marked by 2460409.2849 JD and 2460409.2884 JD.
This setup was attached to a Meade-14 LX200R on a Paramount MX+ equatorial mount to track the sun across the sky.
To transform the livestream into a lightcurve, we needed to extract the percentage of the sun's disk visible in the video frames as the eclipse progressed.
We accomplished this by first grayscaling the image of the eclipse and then using Otsu thresholding to only count pixels above a certain value.
This sucessfully counted the bright sun pixels while ignoring the background noise.
To get the time for each data point, we took an image of the in-video clock at the same time we counted the pixels of the eclipse and used computer vision to recognise the characters in the clock, giving us the time at which the frame was pixel-counted.
The number of pixels of the solar disk over time can then be normalized to a relative brightness.
\paragraph{The Light Sensor Lightcurve}
The light sensor used to collect data during the solar eclipse was the Vernier Light Sensor (LS-BTA) pointed at the sky.
Dr. Todd Abel and Shane Ayotte provided the light sensor data, which we normalized to relative brightness.
Because the light sensor data had timestamps included, we used it to confirm the timing accuracy of our other lightcurves.
\\
Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, where we observed that all three had a very similar shape with heavy overlap between the theoretical and livestream lightcurves.
This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.

### 2025-03-15 sections/theoretical.tex
scaling figures to 0.93/textwidth
Spell check and commas

In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, as shown in Figure \ref{fig:LightcurveComparison}, validating our optical eclipse lightcurve.

@@

\begin{figure}
  \includegraphics[width=0.6\textwidth]{figures/RadiovsTheoretical}
  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
\end{figure}

>>>>

In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
After setting the time, date, and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, as shown in Figure \ref{fig:LightcurveComparison}, validating our optical eclipse lightcurve.

@@

\begin{figure}
  \includegraphics[width=0.93\textwidth]{figures/RadiovsTheoretical}
  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
\end{figure}
